\Large \bf Cyclone: Replication Middleware for NVM Applications

### 2016-09-27 paper/paper.tex
final version.

Next, Figure~\ref{fig:cc_rep} shows the effect of adding a crash
consistent transaction where the application still does nothing but Cyclone
durably remembers the last sequence number and RPC call result (the application
simply returns the received payload). Throughput is now bottlenecked by NVML
allocator performance at just under a million messages a second. The final
result is adding the hash table in the picture with the clients updating the
values of keys already present in the hash table - a stable workload for easy
comparison. As Figure~\ref{fig:app_rep} shows performance stays at the just
under 1M calls a second mark for pure updates. We also show a
pure read only case where the clients only query the value of a key - there is
no replication \emph{nor} any crash consistent transaction applied. It is
interesting to note that the pure read only case is bottlenecked almost at the same
point as the pure replication case of 7 million operations a second.

These results lead us to conclude that Cyclone provides adequate performance
headroom for transparent replication in NVML applications. In fact our current
focus in the light of these results is towards improving application performance
on top of NVML rather than improving the performane of replication in Cyclone.
%NVML is a general purpose library written for a variety of
%substrates including traditional SSD based storage and there is adequate room
%for improvement of performance for applications running on directly attached
%persistent memory with close to DRAM performance.

@@

\section{Conclusion}
Cyclone allows developers to add availability to applications built on top of
libraries such as NVML and achieve good performance on commodity networking
hardware. A key question is whether Cyclone can be used for other applications
such as filesystems ? \emph{We believe that the requirement for scaling across
multiple replication quorums can be satisfied by applications where the scalable
commutativity rule~\cite{scalable_commutativity} applies to common case
primitives.} Although our intitial release of Cyclone will be for
key value style applications, our future research is based on this hypothesis.
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{acm}
\bibliography{paper}

>>>>

Next, Figure~\ref{fig:cc_rep} shows the effect of adding a crash consistent
transaction where the application still does nothing but Cyclone durably
remembers the last sequence number and RPC call result (the application simply
returns the received payload). Throughput is now bottlenecked by NVML allocator
performance at just under a million messages a second. The final result is
adding the hash table in the picture with the clients updating the values of
keys already present in the hash table - a stable workload for easy
comparison. As Figure~\ref{fig:app_rep} shows, performance stays at just under
1M calls a second for pure updates. We also show a pure read only case where the
clients only query the value of a key - there is no replication \emph{nor} any
crash consistent transaction applied. It is interesting to note that the pure
read only case is bottlenecked almost at the same point as the pure replication
case of 7 million operations a second, demonstrating the efficiency of Cyclone's
replication under load.

Contrary to common wisdom that replication over commodity networks is expensive,
these results lead us to conclude that Cyclone provides adequate performance
headroom for transparent replication in NVML-based key value maps.
%In fact our current focus in the light of
%these results is towards improving application performance on top of NVML rather
%than improving the performane of replication in Cyclone.
%NVML is a general purpose library written for a variety of
%substrates including traditional SSD based storage and there is adequate room
%for improvement of performance for applications running on directly attached
%persistent memory with close to DRAM performance.

@@

\section{Conclusion}
Cyclone allows developers to add availability to key value maps built on top of
libraries such as NVML and achieve good performance on commodity networking
hardware. A key question is whether Cyclone can be used for other applications
such as filesystems? \emph{We believe that the requirement for scaling across
  multiple replication quorums can be satisfied by applications where the
  scalable commutativity rule~\cite{scalable_commutativity} applies to common
  case primitives.} Although our intitial release of Cyclone will be for key
value style applications, our on-going research is based on the scalable
commutativity hypothesis.
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{acm}
\bibliography{paper}
